SciPy - some descriptive title here

### 2018-04-09 scipy-1.0/scipy-optimize.tex
MAINT: Pinned the location of Table 1 to prevent interjection into asv subsection.
MAINT: Formatting fixes such that optimize and asv sections are not interleaved with other sections.
MAINT: global optimizer

\newcommand{\RR}{\ensuremath{\mathbb{R}}}
The \texttt{scipy.optimize} module provides functions for the numerical solution of several classes of root finding and optimization problems:
\begin{enumerate}
\item nonlinear root finding problems (\texttt{brentq}, \texttt{brenth}, \texttt{ridder}, \texttt{bisect}, \texttt{newton}, and \texttt{root}),
\item linear sum assignment problems (\texttt{linear\textunderscore sum\textunderscore assignment}),
\item linear and nonlinear sum-of-squares problems (\texttt{leastsq}, \texttt{least\textunderscore squares}, \texttt{nnls}, \texttt{lsq\textunderscore linear}, and \texttt{curve\textunderscore fit}),
\item general, linear optimization problems (\texttt{linprog}),
\item general, nonlinear, local optimization problems of a single variable (\texttt{minimize\textunderscore scalar}),
\item general, nonlinear, local optimization problems of several variables (\texttt{minimize}), and
\item general, global optimization problems (\texttt{basinhopping}, \texttt{brute}, \texttt{differential\textunderscore evolution}).
\end{enumerate}
Documentation of SciPy's functionality in each these areas can be found in (cite SciPy documentation), but here we highlight recent additions through SciPy 1.0.

@@

The \texttt{minimize} function provides methods for solving general nonlinear optimization
problems. It unifies several methods with a common interface in order to facilitate
interchanging between solvers with different characteristics.  Table~\ref{tab:minimize} summarizes
all the methods available for solving minimization problems of the type:
\begin{equation}
  \label{eq:minimization-prob}
  \min_x f(x)
\end{equation}
where $f$ is a multivariate function $f: \mathbb{R}^n \rightarrow \mathbb{R}$ and $x \in \mathbb{R}^n$.
\texttt{COBYLA} and \texttt{SLSQP} methods allow nonlinear constraints to be included in the optimization
problems, \texttt{L-BFGS-B} and \texttt{TNC} allow box constraints $x^l \le x \le x^u$,
and the remaining methods are unconstrained optimization methods.

\begin{table}[]

@@

The method \texttt{trust-krylov}, introduced in the latest release, is as a good compromise between
\texttt{trust-ncg} and \texttt{trust-exact}: it provides a more accurate solution to the trust-region
subproblem than \texttt{trust-ncg} but does not require the Hessian to be stored and factored as in \texttt{trust-exact}.

>>>>

\newcommand{\RR}{\ensuremath{\mathbb{R}}}
The \texttt{scipy.optimize} module provides functions for the numerical solution of several classes of root finding and optimization problems:
\begin{enumerate}
\item nonlinear root finding problems (\texttt{brentq}, \texttt{brenth}, \texttt{ridder}, \texttt{bisect}, \texttt{newton}, and \texttt{root}),
\item linear sum assignment problems (\texttt{linear\textunderscore sum\textunderscore assignment}),
\item linear and nonlinear sum-of-squares problems (\texttt{leastsq}, \texttt{least\textunderscore squares}, \texttt{nnls}, \texttt{lsq\textunderscore linear}, and \texttt{curve\textunderscore fit}),
\item general, linear optimization problems (\texttt{linprog}),
\item general, nonlinear, local optimization problems of a single variable (\texttt{minimize\textunderscore scalar}),
\item general, nonlinear, local optimization problems of several variables (\texttt{minimize}), and
\item general, nonlinear, global optimization problems of several variables (\texttt{basinhopping}, \texttt{brute}, \texttt{differential\textunderscore evolution}).
\end{enumerate}
Documentation of SciPy's functionality in each these areas can be found in (cite SciPy documentation), but here we highlight recent additions through SciPy 1.0.

@@

The \texttt{minimize} function provides methods for solving general nonlinear optimization
problems. It unifies several methods with a common interface in order to facilitate
interchanging between solvers with different characteristics.  Table~\ref{tab:minimize} summarizes
the methods available for solving minimization problems of the type:
\begin{equation}
  \label{eq:minimization-prob}
  \min_x f(x)
\end{equation}
where $f$ is a multivariate function $f: \mathbb{R}^n \rightarrow \mathbb{R}$ and $x \in \mathbb{R}^n$.
\texttt{COBYLA} and \texttt{SLSQP} methods allow nonlinear constraints to be included in the optimization
problems, \texttt{L-BFGS-B} and \texttt{TNC} allow box constraints $x^l \le x \le x^u$,
and the remaining methods are unconstrained optimization methods.

The method \texttt{trust-krylov}, introduced in the latest release, is a good compromise between
\texttt{trust-ncg} and \texttt{trust-exact}: it provides a more accurate solution to the trust-region
subproblem than \texttt{trust-ncg} but does not require the Hessian to be stored and factored as in \texttt{trust-exact}.

\begin{table}[H]

@@

% Some problems may require the use of global optimizers to find the minimum of the objective function over the set of all parameter values, especially if the objective function possesses many local minima that other solvers could get stuck in.
% \texttt{Basinhopping} \cite{Wales1997} uses random perturbation of the parameter vector, with local minimization. The acceptance of the new coordinates is dictated by the Metropolis test typically used in Monte Carlo simulations.
% \texttt{differential\textunderscore evolution} uses
